---
title: "Writing a paper with R and Quarto 1.4 about municipality level correlation of night lights (by satellites) and poverty risk in Finland"
author:
  - name: Christian Hakulinen
    corresponding: true
    orcid: 0000-0001-8629-9960
    affiliations:
      - ref: helsinki
      - ref: thl
  - name: Ripsa Niemi
    affiliations:
      - ref: helsinki
  - name: Mai Gutvilig
    affiliations:
      - ref: helsinki
  - name: Kimmo Suokas
    orcid: 0000-0001-6296-6343
    email: kimmo.suokas@helsinki.fi
    affiliations:
      - ref: tuni
      - ref: helsinki
affiliations: 
  - id: helsinki
    name: University of Helsinki, Department of Psychology and Logopedics, Faculty of Medicine
    address: PO Box 21 (Haartmaninkatu 3)
    postal-code: 00014
    city: Helsinki
    country: Finland
  - id: thl
    name: National Institute for Health and Welfare
    department: Department of Health and Social Care Systems
    city: Helsinki
    country: Finland
  - id: tuni
    name: Tampere University, Faculty of Social Sciences
    address: 
    country: Finland
execute:
  echo: false
  warning: false
fig-dpi: 600
crossref:
  custom:
    - kind: float
      reference-prefix: Table S
      key: supptbl
      space-before-numbering: false
    - kind: float
      reference-prefix: Figure S
      key: suppfig
      space-before-numbering: false
format: docx
filters:
  - authors-block
  - docx-landscape.lua
editor: 
  markdown: 
    wrap: 72
bibliography: references.bib
csl: american-medical-association.csl
---

```{r general_settings}
#| warning: false
library(here)
library(data.table)
library(ggplot2)
library(ggrepel)
library(ggtext)
library(ggpubr)
library(stringr)
library(patchwork)
library(flextable)

numb <- function(x, n_decim=2, big_mark = ' '){
  #format(as.numeric(sprintf(paste0("%.", n_decim, "f"), x)), big.mark = big_mark)
  formatC(x, big.mark = big_mark, decimal.mark = "·", digits = n_decim, format = 'f')
  }

theme_set(theme_void())

footnote_symbols <- c("†", "‡", "§", "¶", letters)

```

```{r results_in}
source(here("R", "11_results.R"))

```

```{r tables_data}

tbl_mokit <- list()
tbl_mokit$n_rows <- 10
tbl_mokit$top <- kunnat %>% as.data.table() %>% .[order(-mokit_lkm),.(nimi, mokit = mokit_lkm)] %>% head(tbl_mokit$n_rows)
tbl_mokit$bottom <- kunnat %>% as.data.table() %>% .[order(-mokit_lkm),.(nimi, mokit = mokit_lkm)] %>% tail(tbl_mokit$n_rows)

tbl_nl <- list()
tbl_nl$n_rows <- 12
tbl_nl$tbl <- kunnat %>% as.data.table() %>% .[order(-lights_mean),.(nimi, lights_mean)] %>% head(tbl_nl$n_rows)

```

```{r results_to_text}

to_text <- list()

to_text$y <- y
to_text$n_kunnat <- kunnat %>% as.data.table() %>% .[,.N]
to_text$max_nl_kunta <- kunnat %>% as.data.table() %>% .[lights_mean == max(lights_mean)]

to_text$max_mokit_nimi <- tbl_mokit$top[1, nimi] 
to_text$max_mokit_n <- tbl_mokit$top[1, mokit] %>% numb(n_decim = 0)

to_text$p_nl <- p_vals$nl %>% numb()
```

```{r dgs}
f2x <- c("f21", "f22", "f23", "f24", "f25", "f28", "f29")
f2x_labs <- c("Schizotypal disorder (F21)", 
              "Persistent delusional disorders (F22)", 
              "Acute and transient psychotic disorders (F23)", 
              "Induced delusional disorder (F24)", 
              "Schizoaffective disorders (F25)", 
              "Other nonorganic psychotic disorders (F28)", 
              "Unspecified nonorganic psychosis (F29)")

tbl_dgs <- data.table(
  levels = c("any","any_psy", 
             "f0", "f00_f03", "f04_f09", 
             "f1", 
             "f2", "f20", "f2_no_sch", 
             f2x,
             "f3", "f30_f31", "f32_f33", "f3_other", 
             "f4", "f40_f41", "f42", "f4_other", 
             "f5", #"f50", "f51", "f53", "f5_other", 
             "f6", "f7", "f8", "f9", "f90", "f9_other"),
             #, "psychoses"),
  labs = c("Any mental disorder","Any mental disorder", 
             "Organic mental disorders (F0)", "Dementias (F00-03)", "Other (F04-09)", 
             "Substance use disorders (F1)", 
             "Schizophrenia spectrum (F2)", "Schizophrenia (F20)", "Other (F21-29)", 
           f2x_labs,
             "Mood disorders (F3)", "Mania and bipolar disorder (F30-31)", 
             "Depressive disorders (F32-F33)", "Other (F34-F39)", 
             "Neurotic, stress-related and somatoform disorders (F4)", "Anxiety disorders (F40-41)",
             "Obsessive - compulsive disorder (F42)", "Other (F43-48)", 
             "Behavioural syndromes (F5)", #"f50", "f51", "f53", "f5_other", 
             "Personality disorders (F6)", 
             "Mental retardation (F7)", "Disorders of psychological development (F8)",
             "Behavioural and emotional disorders (F90-98)", "ADHD (F90)", "Other (F91-98)")
           #, "All psychoses")
)

tbl_dgs[, subgr := labs %>% str_detect("\\(F\\d\\d")]
tbl_dgs[levels == "f9", subgr := F]

```

ORCID or the main author:

**Data availability statement:** The data that support the findings of
this study are available from the National Institute of Health and
Welfare ([www.thl.fi](https://thl.fi/fi/)) and Statistics Finland
([www.stat.fi](https://www.stat.fi/)). Restrictions apply to the
availability of these data, which were used under license for this
study. Inquiries about secure access to data should be directed to data
permit authority Findata ([findata.fi/en](https://findata.fi/en/)).

**Funding statement:** Kimmo Suokas was supported by the Jalmari and
Rauha Ahokas Foundation and the Finnish Psychiatric Association.
Christian Hakulinen was supported by the Academy of Finland (354237) and
the European Union (ERC, MENTALNET, 101040247). Views and opinions
expressed are however those of the authors only and do not necessarily
reflect those of the European Union or the European Research Council.
Neither the European Union nor the granting authority can be held
responsible for them.

**Conflict of interest disclosure:** We declare no competing interests.

**Ethics approval statement:** The Research Ethics Committee of the
Finnish Institute for Health and Welfare approved the study protocol
(decision #10/2016§751).

**Patient consent statement:** Informed consent is not required for
register-based studies in Finland.

**Acknowledgments:**

\newpage

## Abstract

**Objectives:** Night lights have been used as a proxy measure for
economic circumnstances. Let's write a paper about it.

**Methods:** We drew colorful figures and studied correlations.

**Results:** Overall, there are `r to_text$n_kunnat` municipalities.
Municipality with most cottages is `r to_text$max_nl_kunta[,nimi]`. The
greatest number of catteges is in `r to_text$max_mokit_nimi`,
`r to_text$max_mokit_n`. P-values was `r to_text$p_nl`.

**Conclusions:** No correlation found. Quarto 1.4, published 24 Jan
2024, seems like a big step.

**Keywords:** Satellites, holydays, psychiatry, epidemiology

\newpage

## Introduction

But I must explain to you how all this mistaken idea of denouncing
pleasure and praising pain was born and I will give you a complete
account of the system, and expound the actual teachings of the great
explorer of the truth, the master-builder of human happiness. No one
rejects, dislikes, or avoids pleasure itself, because it is pleasure,
but because those who do not know how to pursue pleasure rationally
encounter consequences that are extremely painful. Nor again is there
anyone who loves or pursues or desires to obtain pain of itself, because
it is pain, but because occasionally circumstances occur in which toil
and pain can procure him some great pleasure. To take a trivial example,
which of us ever undertakes laborious physical exercise, except to
obtain some advantage from it? But who has any right to find fault with
a man who chooses to enjoy a pleasure that has no annoying consequences,
or one who avoids a pain that produces no resultant pleasure. This is a
1914 translation by H. Rackham, <https://www.lipsum.com>.

Citation to an important paper.[@suokas]

## Method

We used R with Quarto 1.4 to to do this. See:
<https://quarto.org/docs/blog/posts/2024-01-24-1.4-release/>

### Analysis

We used average masked Visible Infrared Imaging Radiometer Suite (VIIRS)
in `r y` by [Colorado School of
Mines](https://eogdata.mines.edu/nighttime_light/), Statistics Finland
data, accessed using `library(pxweb)`, and municipality data, accessed
using `library(geofi)`.

## Results

Overall, there are `r to_text$n_kunnat` municipalities. Municipality
with most cottages is `r to_text$max_nl_kunta[,nimi]`. The greatest
number of catteges is in `r to_text$max_mokit_nimi`,
`r to_text$max_mokit_n`. P-values was `r to_text$p_nl`.

See @tbl-mokit. See @fig-nl also. More in @supptbl-mokit.

The brightest municipalites are in @tbl-nl.

### Additional analyses

See @suppfig-mp. See @suppfig-cp.

## Discussion

We found no correlations but we drew colorful figures.

The main pro is easy editing.

-   Minor changes in the analyses well be updated automatically.

-   References to Tables and Figures. Custom Float Cross-Reference (1.4)

-   Authors list

<https://quarto.org/docs/authoring/front-matter.html>

### Limitations

There are some painful steps in this workflow.

-   Using Mac may be problematic (Quarto 1.3).

-   Formatting docx is difficult. Landscape pages, complex tables,
    figure size, etc.

    -   <https://github.com/kapsner/authors-block> for title page

    -   Custom solution for landscape
        <https://stackoverflow.com/questions/73784720/changing-page-orientation-in-word-using-quarto>

    -   you can use docx templates..

### Conclusions and future

Quarto 1.4, published 24 Jan 2024, brought ease to this workflow. It
comes with manuscript projects, dashboards and Typst, among other
things. It might turn out a big step, we well see.

[Typst](https://github.com/typst/typst) is a new open-source
markup-based typesetting system that is designed to be as powerful as
LaTeX while being much easier to learn and use.

Read more:

-   <https://mine.quarto.pub/manuscripts-conf23/>

-   <https://quarto.org/docs/manuscripts/authoring/rstudio.html>

\newpage

## Conflict of Interest Statement

## Other stuff if not in the beginning

\newpage

## References

::: {#refs}
:::

\newpage

## Tables

### @tbl-mokit. Municipalities with the highest number of cottages

::: {#tbl-mokit}
```{r}
span <- "Top"
#tbl_mokit$col_lab <- paste0("Cottages", "<sup>", footnote_symbols[1], "</sup>" ,", N")
nimi_lab <- "Name"

tbl_mokit$top %>% 
  .[, .(nimi, n = mokit %>% numb(n_decim = 0))] %>% 
  flextable() %>% 
  set_header_labels(
    values = list(nimi = nimi_lab, n = tbl_mokit$col_lab)
    ) %>% 
  add_header_row(values = paste(span, tbl_mokit$n_rows), colwidths = 2) %>% 
  autofit() %>% 
  compose(i = 2, j = 2, part = "header", value = as_paragraph("Cottages", as_sup(footnote_symbols[1]), ", N") ) %>% 
  theme_apa()

```
:::

^`r footnote_symbols[1]`^All colors included.

\newpage

### @tbl-nl. The top `r tbl_nl$n_rows` brightest municipalities

::: {#tbl-nl}
```{r}

col_lab <- "Mean night light"

tbl_nl$tbl %>% 
  .[, .(nimi, n = lights_mean %>% numb(n_decim = 0))] %>% 
  flextable() %>% 
  set_header_labels(
    values = list(nimi = nimi_lab, n = col_lab)
    )  %>% 
  autofit() %>% 
  theme_apa()

```
:::

## Figures

### @fig-nl. Night lights in Finland in `r to_text$y`

```{r}
#| label: fig-nl
#| fig-height: 12
#| fig-width: 20

fig_labs <- list()
fig_labs$mokit <- "Cottages, N"
fig_labs$pienituloisuusaste <- "At risk of poverty, %"
fig_labs$nl <- "Mean night lights"

figs$nl_kunnat + (figs$mokit +labs(fill = fig_labs$mokit)) + (figs$pienituloisuus + labs(fill = fig_labs$pienituloisuusaste)) +plot_annotation(tag_levels = 'a')

```

\newpage

### @fig-mp. Association of night lights and poverty

::: {#fig-mp}
```{r}
#| warning: false
#| fig-height: 4
#| fig-width: 6

scttr$tulot_nl+ labs(y = fig_labs$pienituloisuusaste, x = fig_labs$nll)
```
:::

\newpage

## Supplementary Tables

### @supptbl-mokit Municipalities with the lowest number of cottages

::: {#supptbl-mokit}
```{r}

span <- "Bottom"

tbl_mokit$bottom %>% 
  .[order(mokit)] %>% 
  .[, .(nimi, n = mokit %>% numb(n_decim = 0))] %>% 
  flextable() %>% 
  set_header_labels(
    values = list(nimi = nimi_lab, n = tbl_mokit$col_lab)
    ) %>% 
  add_header_row(values = paste(span, tbl_mokit$n_rows), colwidths = 2) %>% 
  autofit() %>% 
    compose(i = 2, j = 2, part = "header", value = as_paragraph("Cottages", as_sup(footnote_symbols[1]), ", N") ) %>% 
  theme_apa()

```
:::

^`r footnote_symbols[1]`^All colors included.

\newpage

## Supplementary Figures

### @suppfig-mp. Association of number of cottages and night lights

::: {#suppfig-mp}
```{r}
#| warning: false
#| fig-height: 4
#| fig-width: 6

scttr$tulot_mokit+ labs(y = fig_labs$mokit, x = fig_labs$pienituloisuusaste)
```
:::

\newpage

### @suppfig-cp. Association of number of cottages and poverty

::: {#suppfig-cp}
```{r}
#| warning: false
#| fig-height: 4
#| fig-width: 6

scttr$tulot_mokit+ labs(y = fig_labs$mokit, x = fig_labs$pienituloisuusaste)
```
:::
