---
title: "Reproducible workflow for scientific writing with R"
author: "Kimmo Suokas"
date: 2024-02-09
format:
  revealjs:
    progress: true
    history: true
---

```{r}
#| warning: false
library(here)
library(data.table)
library(ggplot2)
library(ggrepel)
library(ggtext)
library(ggpubr)
library(stringr)
library(patchwork)
library(gt)

source(here("R", "11_results.R"))

```

```{r}
numb <- function(x, n_decim=2, big_mark = ' '){
  #format(as.numeric(sprintf(paste0("%.", n_decim, "f"), x)), big.mark = big_mark)
  formatC(x, big.mark = big_mark, digits = n_decim, format = 'f')
  }
```

##  {auto-animate="true"}

::: {style="margin-top: 100px;"}
Writing complitely without MS Word
:::

##  {auto-animate="true"}

::: {style="margin-top: 300px; font-size: 1.5em; color: red;"}
Writing complitely without MS Word
:::

::: {.fragment .fade-up}
(almost)
:::

::: {.fragment .fade-right}
A case example:
:::


## [Municipality level correlation of night lights (by satellites) and poverty risk in Finland ]{style="color:orange;"}

Let's use

-   Average masked Visible Infrared Imaging Radiometer Suite (VIIRS) in `r y` by [Colorado School of Mines](https://eogdata.mines.edu/nighttime_light/),
-   Statistics Finland data, accessed using `library(pxweb)`,
-   Municipality data, accessed using `library(geofi)`

## Night lights


```{r}
#| fig-width: 8
#| fig-height: 15

a <- figs$nl 

a
#::: {.column-page layout-ncol="2"}

```

## Night lights 

```{r}
#| fig-width: 16
#| fig-height: 15
b <- figs$nl_kunnat
a + b

```


## Night lights 

```{r}
#| fig-width: 24
#| fig-height: 15
c <- figs$nl_mean+ theme(legend.title = element_text(size=25), legend.text = element_text(size=20))

a + b + c

```



## The brightest municipalities {.r-stretch}

```{r}
kunnat %>% as.data.table() %>% .[order(-lights_mean),.(nimi, lights_mean = lights_mean %>% round(2))] %>% head(10) %>% gt()
```


## Correlation: low income and mean night lights


```{r}
scttr$tulot_nl
```

## Correlation: summer cottages and mean night lights

```{r}
scttr$mokit_nl
```

## Correlation: low income and summer cottages

```{r}
scttr$tulot_mokit 
```

## {auto-animate=true auto-animate-easing="ease-in-out"}


::: {.r-hstack}
::: {data-id="box1" auto-animate-delay="0" style="background: #2780e3; width: 200px; height: 150px; margin: 10px;"}
:::

::: {data-id="box2" auto-animate-delay="0.1" style="background: #3fb618; width: 200px; height: 150px; margin: 10px;"}
:::

::: {data-id="box3" auto-animate-delay="0.2" style="background: #e83e8c; width: 200px; height: 150px; margin: 10px;"}
:::
:::

## {auto-animate=true auto-animate-easing="ease-in-out"}

::: {.r-stack}
:::{data-id="box1" style="background: #2780e3; width: 350px; height: 350px; border-radius: 200px;"}
:::

:::{data-id="box2" style="background: #3fb618; width: 250px; height: 250px; border-radius: 200px;"}
:::

:::{data-id="box3" style="background: #e83e8c; width: 150px; height: 150px; border-radius: 200px;"}
:::
:::

::: {.fragment}
:::{style="text-align: center;"}
Now, let's write the paper
:::
:::

